Dismal Code: Studying the Evolution of Security Bugs

### 2013-03-27 docs/evol.tex
correct correlation matrix

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weekest correlations with the other categories. In general though, the
results show then that bugs do flock together: we do not find projects
with only a certain kind of bug; bugs come upon projects in swarms of
different kinds.
\begin{table}
  \begin{threeparttable}
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \begin{tablenotes}
      \footnotesize
      \item The matrix presents pairwise correlations between the
        following bug categories in order: Security High, Security
        Low, Style, Bad Practice, Correctness, MT Correctness,
        Performance, i18n, Experimental.
    \end{tablenotes}
  \end{threeparttable}
\end{table}

>>>>

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weekest correlations with the other categories. Our results show that
in general bugs do flock together. We do not find projects with only a
certain kind of bug; bugs come upon projects in swarms of different
kinds. Bugs of the {\it Security High} category, though, are
different: they are either not associated with other bugs, or only
weakly so. Perhaps it takes a special kind of blunder to make it a
security hazard.
\begin{table}
  \begin{threeparttable}
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \begin{tablenotes}
      \footnotesize
      \item The matrix presents pairwise correlations between the
        following bug categories in order: Security High, Security
        Low, Style, Bad Practice, Correctness, MT Correctness,
        Performance, i18n, Experimental.
    \end{tablenotes}
  \end{threeparttable}
\end{table}
